%-------------------------
% Resume -- MERN Stack Focus
%-------------------------

\documentclass[letterpaper,10pt]{article}
\input{../shared/preamble}

\begin{document}

\input{../shared/header}

%--------------SUMMARY-----------------
\section{Summary}
\resumeSubHeadingListStart
\item{}
Full-stack developer with hands-on experience building end-to-end web and mobile applications. Proficient in the MERN stack (MongoDB, Express.js, React, Node.js) with a solid understanding of REST API design, database modeling, and real-time communication via WebSockets. Passionate about building scalable, maintainable systems with clean architecture.
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]
\small{
\item \textbf{Languages:} JavaScript, TypeScript, Dart, C/C++
\item \textbf{Frontend:} React.js, HTML5, CSS3
\item \textbf{Backend:} Node.js, Express.js, REST APIs, WebSockets
\item \textbf{Databases:} MongoDB, Firebase, SQLite
\item \textbf{Architecture:} MVVM, Clean Architecture, MVC
\item \textbf{Tools:} Git, GitHub, VS Code, Postman, Android Studio
}
\end{itemize}

\input{../shared/experience_fullstack}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{QuestAI -- Full-Stack AI Agent}}{}
\resumeItemListStart
\resumeItem{Built a full-stack AI-powered system with React frontend and Node.js/Express backend for real-time agent interaction.}
\resumeItem{Implemented WebSocket-based streaming for low-latency AI response delivery to the browser client.}
\resumeItem{Designed a fault-tolerant backend architecture with error recovery and session persistence using MongoDB.}
\resumeItem{Integrated third-party AI APIs with request queuing and rate-limit handling.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Subject Mastery} $|$ \href{https://play.google.com/store/apps/details?id=com.sanjay_tube.sanjay_ube}{\faAndroid\ Play Store}}{}
\resumeItemListStart
\resumeItem{Built REST API-driven mobile application with authentication flows and secure session handling.}
\resumeItem{Integrated MongoDB-backed content delivery endpoints with efficient data modeling and indexing.}
\resumeItem{Implemented ML-based detection features via REST service integration for assessment integrity.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Sattelite} $|$ \href{https://play.google.com/store/apps/details?id=com.financial.verifier.app.app}{\faAndroid\ Play Store}}{}
\resumeItemListStart
\resumeItem{Designed local-first data layer using sqflite and Hive, mirroring patterns used in MongoDB document storage.}
\resumeItem{Built dynamic PDF report generation pipeline, applying data transformation concepts core to backend development.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\input{../shared/education}

\end{document}
