%-------------------------
% Resume -- Backend Focus (Node.js / Express)
%-------------------------

\documentclass[letterpaper,10pt]{article}
\input{../shared/preamble}

\begin{document}

\input{../shared/header}

%--------------SUMMARY-----------------
\section{Summary}
\resumeSubHeadingListStart
\item{}
Software Development Engineer with experience in designing and integrating RESTful APIs, managing data pipelines, and building fault-tolerant server-side systems. Strong foundation in clean architecture principles, database integration (MongoDB, Firebase, SQLite), and real-time communication. Experienced in shipping production-grade features with robust error handling and performance optimization.
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]
\small{
\item \textbf{Languages:} JavaScript, TypeScript, Dart, C/C++, Python
\item \textbf{Backend:} Node.js, Express.js, REST APIs, WebSockets
\item \textbf{Databases:} MongoDB, Firebase, SQLite (sqflite), Hive
\item \textbf{Architecture:} Clean Architecture, MVVM, MVC
\item \textbf{Tools:} Git, GitHub, Postman, VS Code, Jira
\item \textbf{Other:} JWT authentication, CRUD API design, cron scheduling, rate limiting
}
\end{itemize}

\input{../shared/experience}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{QuestAI -- AI Agent Backend}}{}
\resumeItemListStart
\resumeItem{Designed and built a resilient Node.js/Express backend serving AI agent capabilities over WebSocket and HTTP.}
\resumeItem{Implemented WebSocket-based streaming for real-time response delivery with connection lifecycle management.}
\resumeItem{Architected fault-tolerant request pipeline with retry logic, graceful degradation, and session persistence.}
\resumeItem{Integrated third-party AI APIs with rate-limit handling, request queuing, and structured error responses.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Random Alarm App -- Backend}}{}
\resumeItemListStart
\resumeItem{Designed and built a Node.js/Express backend for a random alarm scheduling application from scratch.}
\resumeItem{Implemented RESTful APIs for alarm creation, retrieval, update, and deletion with full CRUD support.}
\resumeItem{Managed alarm scheduling logic server-side with persistent storage in MongoDB and time-zone-aware trigger handling.}
\resumeItem{Structured codebase following MVC architecture with clean separation of routes, controllers, and data models.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Subject Mastery} $|$ \href{https://play.google.com/store/apps/details?id=com.sanjay_tube.sanjay_ube}{\faAndroid\ Play Store}}{}
\resumeItemListStart
\resumeItem{Integrated Firebase backend for authentication, session management, and content delivery.}
\resumeItem{Built and exposed CRUD endpoints for user data, course content, and assessment records via REST APIs.}
\resumeItem{Implemented secure API consumption with structured error handling, input validation, and retry mechanisms.}
\resumeItem{Incorporated ML-based assessment integrity features via backend service integration.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\input{../shared/education}

\end{document}
