%-------------------------
% Resume -- Frontend Focus (React / Flutter UI)
%-------------------------

\documentclass[letterpaper,10pt]{article}
\input{../shared/preamble}

\begin{document}

\input{../shared/header}

%--------------SUMMARY-----------------
\section{Summary}
\resumeSubHeadingListStart
\item{}
Frontend-focused developer with 1.5+ years of experience building responsive, high-performance UIs for mobile and web. Deep expertise in Flutter widget systems, state management (Provider, Riverpod), and component-driven architecture. Experienced in designing accessible, user-friendly interfaces, optimizing rendering performance, and delivering polished cross-platform experiences.
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]
\small{
\item \textbf{Languages:} Dart, JavaScript, TypeScript, C/C++
\item \textbf{UI Frameworks:} Flutter, React.js
\item \textbf{State Management:} Provider, Riverpod, setState, React Hooks
\item \textbf{Styling:} Material Design, Custom Theming, Responsive Layouts
\item \textbf{Architecture:} MVVM, Clean Architecture, Component-Driven Design
\item \textbf{Tools:} Git, GitHub, Android Studio, VS Code, Figma
}
\end{itemize}

\input{../shared/experience}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Subject Mastery} $|$ \href{https://play.google.com/store/apps/details?id=com.sanjay_tube.sanjay_ube}{\faAndroid\ Play Store}}{}
\resumeItemListStart
\resumeItem{Designed and built a pixel-perfect, scalable UI following clean architecture and MVVM separation of concerns.}
\resumeItem{Implemented complex interactive components including real-time quiz flows, progress tracking, and animated transitions.}
\resumeItem{Optimized widget rebuild cycles and rendering performance for smooth UX across low-end Android devices.}
\resumeItem{Integrated ML-based proctoring UI with seamless camera overlay and real-time status feedback.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Sattelite} $|$ \href{https://play.google.com/store/apps/details?id=com.financial.verifier.app.app}{\faAndroid\ Play Store}}{}
\resumeItemListStart
\resumeItem{Built a fully offline UI with intuitive document scanning flows and structured data review screens.}
\resumeItem{Designed dynamic PDF preview and export interface with custom layout rendering using the \texttt{pdf} package.}
\resumeItem{Ensured responsive layouts and accessible UX across varying screen sizes and orientations.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{QuestAI -- AI Agent Interface}}{}
\resumeItemListStart
\resumeItem{Built a real-time chat-style React frontend for AI agent interaction with streaming response rendering.}
\resumeItem{Implemented optimistic UI updates and WebSocket event handling for low-latency user feedback.}
\resumeItem{Designed a clean, minimal component system for message threading, loading states, and error displays.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\input{../shared/education}

\end{document}
