%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Development Engineer - I}{Oct 2025 -- Present}
{Sanora India Pvt Ltd}{}
\resumeItemListStart
\resumeItem{Designed and developed RESTful APIs for authentication, content delivery, and real-time data synchronization using Node.js and Express.js.}
\resumeItem{Built and maintained both frontend UI components and backend services, delivering full-stack features across 2 live production applications.}
\resumeItem{Implemented clean architecture patterns (MVVM, MVC) on both client and server side, ensuring modular, testable, and maintainable codebases.}
\resumeItem{Contributed 15+ major features and 10,000+ lines of production code; resolved 100+ critical bugs across frontend and backend layers.}
\resumeItem{Optimized API response times and server-side performance through profiling, query optimization, and architectural improvements.}
\resumeItemListEnd

\resumeSubheading
{Associate Software Developer}{Oct 2024 -- Oct 2025}
{SwaLay Digital}{}
\resumeItemListStart
\resumeItem{Integrated RESTful APIs for data fetching, user authentication, and real-time content delivery in cross-platform applications.}
\resumeItem{Implemented state management solutions (Provider, Riverpod) and collaborated on backend service integration workflows.}
\resumeItem{Optimized application performance and reduced build times through code refactoring, profiling, and best practices.}
\resumeItemListEnd

\resumeSubHeadingListEnd
